### 2017-09-28 Draft/4-homework20170925.tex
update

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 3\\Monday, September 11, 2017}\bigskip
\end{center}

@@

\begin{center}
\emph{Homework 3 is due by midnight, Friday, September 22.}
\end{center} 
\medskip

\begin{enumerate}
\item  (Problem 34, Page 53) Show that there is a continuous, strictly increasing function on the interval $[0, 1]$ that maps a
set of positive measure onto a set of measure zero.

@@

\textbf{Solution:}
Let $C$ be the Cantor set on $[0, 1]$, and $\varphi(x)$ be the Cantor function. Define
$$
\phi(x) = \varphi(x)+x, ~x\in C.
$$
We now show $\phi^{-1}(x)$, the inverse of $\phi(x)$, satisfies the properties in the problem.
First, since $\phi(x)$ is a continuous, strictly increasing function on $[0, 1]$, thus is continuous and strictly increasing on $C\subset [0, 1]$.

Denote $D = \phi(C)$, then according to theorems in the book, $m(D) = 1$. $\forall x_1 < x_2\in D$, if $\phi^{-1}(x_1) \ge \phi^{-1}(x_2)$, then since $\phi$ is strictly increasing, $\phi(\phi^{-1}(x_1)) = x_1+\phi^{-1}(x_1) \ge \phi(\phi^{-1}(x_2)) = x_2+\phi^{-1}(x_2)$, which means $\phi^{-1}(x_1) < \phi^{-1}(x_2)$, leading to a contradictory. Thus $\phi^{-1}$ is strictly increasing.

On the other hand, $\forall x_0 \in D, \forall \epsilon > 0$, we need to show that $\exists\delta > 0, ~\forall x_1\in D, ~|x_1-x_{0}| < \delta$, then $|\phi^{-1}(x_1)-\phi^{-1}(x)| < \epsilon$. Denote $y_1 = \phi(\min\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\}), ~y_2 = \phi(\max\{(\phi^{-1}(x_0)-\epsilon, ~\phi^{-1}(x_0)+\epsilon)\cap C\})$, then let $\delta = \min{y_1-x_0, y_2-x_0}$, we have $\forall |x-x_0|< \delta$, $|\phi^{-1}(x)-\phi^{-1}(x_0)| < \epsilon$. Thus $\phi^{-1}$ is continuous on $D$.

Since $C$ is measure zero, we get a function satisfying the properties in the problem.
\bigskip

\item (Problem 37, Page 53) Let $f$ be a continuous function defined on $E$. Is it true that $f^{-1}(A)$ is always measurable if $A$ is measurable?

@@

\textbf{Solution:} It is not true.

We may consider the function $\psi(x)$ defined by Proposition 21 on Page 52. It is a strictly increasing continuous function, and it maps a measurable set $A\subset C$, onto a nonmeasurable set. Thus if we consider $\psi^{-1}(x)$, it has been proved as a strictly increasing continuous function in Problem 1. Then $\psi^{-1}(A)$ is nonmeasurable.

\bigskip

\item  (Problem 39, Page 53) Let $F$ be the subset of $[0, 1]$ constructed in the same manner as the Cantor set except that
each of the intervals removed at the nth deletion stage has length $\alpha 3^{-n}$ with $0 < a < 1$. Show
that $F$ is a closed set, $[0, 1]\sim F$ dense in $[0,1]$, and $m(F) = 1- a$. Such a set F is called a \emph{generalized Cantor set}.

@@

\textbf{Solution:}
First, we denote $F_1 = \left[0, \frac{3-\alpha}{6}\right]\cup \left[1-\frac{3-\alpha}{6}, 1\right]$. With the same process of constructing the Cantor set, we have a collection of $F_n$. We define the generalized Cantor set as 
$$
F = \bigcap_{k=1}^{\infty}F_n.
$$
Since each $F_n$ is a closed set, we have $F$ as well closed. Then $F_n$ is the disjoint of union of $2^n$ intervals, each of length $(1-\alpha)\frac{1}{2^n}+\frac{\alpha}{3^n}$. By the finite additivity of Lebesgue measure, 
$$
m(F_k) = 1-\alpha + \left(\frac{2}{3}\right)^n\alpha.
$$
According to the continuity of measure, we have $m(F) = \lim_{k\to\infty}m(F_k) = 1-\alpha$.

Let $x < y\in [0, 1]$. If $y\notin F_k$ for one of the $k$, then since $[0, 1]\setminus F$ is open, there exists $t < y$ in $N(y)$, s.t. $t\in [0, 1]\setminus F$. If $x\notin F_k$, it is the same case. Now we assume that $x, ~y \in F$. If $x, ~y$ are not in the same subset of $F_k$, then $\exists t\in [0, 1]\setminus F$. Then we can assume that $x, ~y$ always belong to the same subset. However, the subsets make a nested set with the limit of lower bound and the upper bound be the same. According to Nested Set Theorem, we have $x = y$. Then we have proved that $[0, 1]\setminus F$ is dense.
\bigskip

\item Let $C$ be the Cantor set and let $\varphi$ be the Cantor-Lebesgue function.
\begin{enumerate}
\item Show that $C$ consists of all $x\in [0,1]$ whose  ternary expansion has coefficients equal to $0$ or $2$, i.e., if $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0, 1, \text{or } 2$, then $x\in C$ if and only if $c_k = 0 \text{ or } 2$. 
\item Show that if $x\in C$ and $x = \sum_{k\geq 1} c_k3^{-k}$, where each $c_k = 0 \text{ or } 2$, then $\varphi(x) = \sum_{k\geq 1} (\frac{1}{2} c_k) 2^{-k}$.
\end{enumerate}
\bigskip
\textbf{Collaborators:}\\
\smallskip

\textbf{Solution:}
\textbf{(a).} We show by induction that a number belongs to the intervals we removed in each step iff its ternary expasion has a coefficient 1. First, the interval removed at the first step can be represented as $(0.1, ~0.2)$. Thus $0.1 \notin F$, and $0.0, 0.2\in F$. Assume it holds in the first $n$ steps, then the intervals removed at the $n+1$ step has the representation $(0.a_1a_2\cdots a_n1, ~0.a_1a_2\cdots a_n2)$, in which $a_i\in\{0, 2\}$. Then each number in this interval has an expansion like
$$
0.a_1a_2\cdots a_n1a_{n+1}\cdots.
$$
Thus each number in $F$ has a coefficient 1 in its expansion.
According to the construction process, we can also know that the reverse also holds. Thus the proposition holds.

\textbf{(b)}. 
% According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step. Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
First, assume $x\in O$. According to the construction of Cantor function, if $x = \sum_{k} c_k3^{-k}$ is the ternary expansion of $x$, and the first $1$ in the ternary expansion is in the $n_{th}$ place, then $\varphi(x) = \frac{1}{2^n} + \sum_{k < n}\frac{1}{2}c_k 2^{-k} $.

If $x = \sum_{k}c_k3^{-k}\in C$, according to the extension of $\varphi(x)$, $\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} $. We can construct a sequence $\{t_i\} = \{\sum_{k} d_k3^{-k}\}$, s.t. $d_i = c_i, \forall i < m_{i+1} $, where $m_i $ is the position of $i_{th}~ 2~ \text{in}~ c_k $, and $d_{m_{i+1}} = 1, ~d_{k} = 0, ~\forall k > m_{i+1}$. Then $\{t_i\}$ is a strictly increasing sequence, and $\lim_{i\to\infty}t_{i} = x$.

Since $\varphi(x)$ is a strictly increasing function in $O$, we know that
$$
\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} \ge \varphi(t_i) = \frac{1}{2^i}+\sum_{k<i}\frac{1}{2}d_k2^{-k}.
$$ 
Thus 
$$
\varphi(x) \ge \sum_{k}\frac{1}{2}c_k2^{-k} 
$$
when we let $i\to\infty$. On the other hand, $\forall \epsilon > 0$, $\exists i > 0$, $\frac{1}{2^i} < \epsilon$. Thus
$$
\varphi(t_i) > \sum_{k}\frac{1}{2}c_k2^{-k} - \epsilon.
$$ 
So 
$$
\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} = \sum_{k}\frac{1}{2}c_k2^{-k}.
$$
\bigskip

\item  Construct a Cantor-type subset of $[0,1]$ by removing from each interval remaining at the $k^{\text{th}}$ stage, a subinterval of relative length $\theta_k$, $0 < \theta_k < 1$. Show that the remainder has measure zero if and only if $\sum_{k\geq 1} \theta_k = \infty$.  (Use the fact that for $a_k > 0$, the product $\Pi_{k = 1}^{\infty} a_k$ converges, in the sense that $\lim_{n\to \infty} \Pi_{k=1}^N a_k$ exists and  is not zero, if and only if $\sum_{k =1}^{\infty} \ln a_k$ converges.)

@@

\textbf{Solution:}
Denote $F_n$ as the remained set after $n$ steps. Then according to the construction, we have 
$$
m(F_n) = \prod_{i=1}^{n}(1-\theta_i).
$$
First we have $\sum_{n=1}^{\infty}-\theta_n$ and $\sum_{n=1}^{\infty}\ln(1-\theta_n)$ be both negative-term series, and the necessity of their convergence is $\lim_{n\to\infty}\theta_n = 0$. On the other hand, when $\lim_{n\to\infty} \theta_n = 0$, 
$$
\lim_{n\to\infty}\frac{\ln(1-\theta_n)}{-\theta_n} = 1,
$$
thus that $\sum{\ln(1-\theta_n)}$ converges is equivalent to the convergence of $\sum{-\theta_n}$.

Then according to the continuity of measure,
$$
\begin{aligned}
m(F) > 0 \Leftrightarrow m(\lim_{n\to\infty}F_n) > 0 \Leftrightarrow \prod_{i=1}^{\infty}(1-\theta_i) ~\text{converges} \Leftrightarrow \sum_{i=1}^{\infty} \ln(1-\theta_i) ~\text{converges} \\
\Leftrightarrow \sum_{i=1}^{\infty}\theta_i ~\text{converges}.
\end{aligned}
$$
Thus $m(F) = 0$ iff $\sum{\theta_i} = \infty$.

\bigskip

\item Let $Z$ be a set of measure zero in $\mathbb{R}$.  What is the measure of $\{x^2 \mid x\in Z\}$?

@@

\textbf{Solution:}
$X = \{x^2\mid x\in Z\}$ is also measure 0.

First, if the set $Z$ is bounded, which means $Z\in [0, M]$. Since $m(Z) = 0$, $\forall \epsilon > 0$, there exists an open cover $\{O_i\} = \{(a_i, b_i)\}$, s.t. $m^*(\cup\{O_i\}\setminus Z) < \epsilon$. Thus $\{(a_i^2, b_i^2)\}$ is an open cover of $X$, and $m^*(\cup(a_i^2, b_i^2)\setminus X) \le M\sum(b_i-a_i) < M\epsilon$. Thus now $X$ is a measure-zero set. When $Z \in [-M, 0]$, with the same process above, we can know that $X$ is a measure-zero set. Then when $Z \in [-M, M]$, we know $X$ is also measure zero.

Since $Z$ is measure zero, for $\forall \epsilon > 0$ and integer $n > 0$, we have $m(Z\cap [-n, n]) < 2^{-n}\epsilon$. Thus from the discussion above we have $m(X\cap [-n^2, n^2]) < 2^{-n}\epsilon$. Since 
$$
X = \bigcup_{n=1}^{\infty}X\cap[-n, n],
$$
with the addivity of measure, 
$$
m(X) < \sum_{n=1}^{\infty}2^{-n}\epsilon = \epsilon.
$$
With the arbitrariness of $\epsilon$, we have $m(X) = 0$.
\bigskip

\item  Let $0.\alpha_1 \alpha_2 \cdots$ be the dyadic development of any $x\in[0,1]$. Let $k_1,k_2,k_3,\ldots$ be a fixed permutation of the positive integers $1,2,\ldots$, and consider the transformation $T$ which sends $x = \alpha_1\alpha_2\alpha_3\cdots$ to $Tx: = \alpha_{k_1}\alpha_{k_2}\alpha_{k_3}\cdots$. Show that if $E$ is a measurable subset of $[0,1]$ then its image under $T$, $T(E)$, is also measurable and that $m(T(E))= m(E)$.  That is, show that $T$ is a measure preserving transformation of $[0,1]$. [Consider first the special case where $E$ is a dyadic interval of the form $(s2^{-k}, (s+1)2^{-k})$ and $s = 0,1,\ldots, 2k-1$.  Then think about open sets and note that each open set can be written as a countable union of non-overlapping half-open dyadic intervals.]

\textbf{Solution:}
Consider the intervals $E_k^i = [i\cdot2^-{k}, ~(i+1)2^{-k})$. Then
$$
T[E_k] = \bigcap_{i=1}^{2^k}F_{k_i},
$$
where 
$$
F_{k_i} = \left\{
\begin{aligned}
&[F_{k_{i-1}}.\text{left}, ~F_{k_{i-1}}.\text{mid}), ~\text{if}~ k_i = 0 \\
&[F_{k_{i-1}}.\text{mid}, ~F_{k_{i-1}}.\text{right}), ~\text{if}~ k_i = 1.
\end{aligned}
\right.
$$
Then since the finite intersection of closed sets is measurable, we know that $T[E_k]$ is measurable, and we have $m(T(E_k)) = m(E_k)$ since the probability of the numbers with infinite length be seperated into the intervals. Then since each open interval can be written as a countable union of non-overlapping half-open dyadic intervals, we know from the discussion above that $T(E)$ is measurable, and $m(T(E)) = m(E)$.

\bigskip

>>>>

\begin{center}
\textbf{Introduction to Analysis $I$\\Homework 4\\Wednesday, September 27, 2017}\bigskip
\end{center}

@@

\begin{center}
\emph{Homework 4 is due by midnight, Saturday, October 7.}
\end{center} 
\medskip

\begin{enumerate}
\item  (Problem 18, Page 63) Let $I$ be a closed bounded interval and let $f$ be a bounded measurable function defined on $I$. Let $\epsilon > 0$.  Show that there is a step function $h$ on $I$ and a measurable subset $F$ of $I$ for which \[
|h-f|< \epsilon \text{ on } F \text{ and } m(I\sim F)< \epsilon .\]

@@

\textbf{Solution:}
\bigskip

\item (Problem 22, Page 64) (Dini's Theorem)  Let $\{f_n\}$ be an increasing sequence of continuous functions on $[a,b]$ which converges pointwise on $[a,b]$ to the continuous function $f$ on $[a,b]$.  Show that the convergence is uniform on $[a,b]$.

@@

\textbf{Solution:}
\bigskip

\item  (Problem 5, Page 364) Show that an extended real-valued function $f$ on $X$ is measurable if and only if for each rational number $c$, $\{x\in X \mid f(x)< c\}$ is a  measurable set.

@@

\textbf{Solution:}
\bigskip

\item (Problem 13, Page 365) Let $\{f_n\}$ be a sequence of real-valued functions on $X$ such that for each natural number $n$, $\mu \{x\in X \mid |f_n (x) - f_{n+1}(x)|> 1/2^n\}<1/2^n$. Show that $\{f_n\}$ is pointwise convergent a.e. on $X$.

@@

\textbf{Solution:}
\bigskip

\item  (Problem 15, Page 365)  A sequence $\{f_n\}$ of measurable real-valued functions on $X$ is said to \emph{converge in measure} to a measurable function $f$  provided that for each $\eta > 0$, \[
\lim_{n\to \infty} \mu\{x\in X \mid |f_n(x) - f(x)|>\eta \} = 0.\]A sequence $\{f_n\}$ of measurable functions is said to be \emph{Cauchy in measure} provided that for each $\epsilon > 0$ and $\eta > 0$, there is an index $N$ such that for each $m,n\geq N$, \[
\mu\{x\in X \mid |f_n(x) - f_m(x)| > \eta \} < \epsilon.\]
\begin{enumerate}
\item Show that if $\mu(X)< \infty$ and if $\{f_n\}$ converges pointwise a.e. on $X$ to a measurable function $f$, then $\{f_n\}$ converges to $f$ in measure.
\item Show that if $\{f_n\}$ converges to $f$ in measure, then there is a subsequence of $\{f_n\}$ that converges pointwise a.e. to $f$.
\item Show that if $\{f_n\}$ is Cauchy in measure, then there is a measurable function $f$ to which $\{f_n\}$ converges in measure.\end{enumerate}

\item (Problem 16, Page 365) Assume $\mu (X) < \infty$.  Show that $\{f_n\}$ converges to $f$ in measure if and only if each  subsequence of $\{f_n\}$ has a further subsequence that converges pointwise a.e. on $X$ to $f$.  Use this to show that for two sequences that converge in measure, the product sequence also converges in measure to the product of the limits.

\item Show that if $f$ is an lower semicontinuous (resp. upper semicontinuous) function on an interval $[a,b]$, then there is a family $\{f_{\alpha}\}$ of continuous functions on the interval $[a,b]$ such that $f(x) = \sup\{f_{\alpha}(x) \mid \alpha \in A \}$ (resp. $f(x) = \inf\{f_{\alpha}(x) \mid \alpha \in A \}$) for all $x \in [a,b]$.

@@

\textbf{Solution:}
\bigskip
